Quality Definitions of Qualities

### 2019-11-06 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
Addition to introduction section to clarify the "template" used for each quality summary/discussion

\wss{Introduce citation conventions.}

>>>>

The pattern in the presentation for each of the qualities is the same.  First we
summarize all of the definitions that we could find in the literature.  To keep
the clutter of quotation marks down, we have adopted the convention that each
definition is given verbatim from the cited source, but without showing
quotation marks.  After the summary of the existing definitions, we propose the
definition that we would like to work with going forward.  This definition can
either be our preference from the existing definitions, or a new definition,
which is often found by combining existing definitions.  Following the proposed
definition is an explanation for the reasoning that led to this choice.
